### 2015-07-08 2015-compmorphon-morphver/poster.tex
fixes to flowchart
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61218 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{tikz}
\usetikzlibrary{shapes,arrows} %for flowchart
% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]
%\usepackage{pgfbaselayers}
%\pgfdeclarelayer{background}
%\pgfdeclarelayer{foreground}
%\pgfsetlayers{background,main,foreground}

@@

\definecolor{bordercol}{RGB}{0,0,0}
%\definecolor{headercolone}{RGB}{6,130,22}
\definecolor{headercol}{cmyk}{1,0.64,0,0.6}
%\definecolor{headercolone}{cmyk}{1,0.64,0,0.6}
%\definecolor{headercoltwo}{cmyk}{0.44,0,0.15,0.17}
%\definecolor{headercolone}{cmyk}{0.3,0,0.15,0.17}
%\definecolor{headercoltwo}{cmyk}{0.3,0,0.15,0.17}
\definecolor{iumint}{cmyk}{0.40,0,0.23,0}
\definecolor{iumidnight}{cmyk}{0.71,0.30,0.13,0.41}
%\definecolor{boxcolor}{RGB}{176,208,223}
%\definecolor{boxcolor}{cmyk}{0.3,0.08,0.08,0.1}
\definecolor{boxcolor}{cmyk}{0.2,0.03,0.03,0.1}
\definecolor{headerfontcol}{RGB}{255,255,255}
\newcommand{\hilitetwo}[1]{{\addfontfeature{Color=99333399}#1}}
\newcommand{\hiliteone}[1]{{\addfontfeature{Color=06821699}#1}}
\newcommand{\hilitegrey}[1]{{\addfontfeature{Color=77777799}#1}}
\newcommand{\hilitelightgrey}[1]{{\addfontfeature{Color=CCCCCC99}#1}}
\newcommand{\hiliteblue}[1]{{\addfontfeature{Color=44697DFF}#1}}

@@

%\usepackage{natbib}
\usepackage[backend=biber,citestyle=apa,style=authoryear,maxbibnames=99,maxcitenames=2]{biblatex}
\bibliography{poster}
\renewcommand*{\nameyeardelim}{\addcomma\space}

@@

		\headerbox{References}{name=references,column=3,below=tuvanvowelharmony}{
			\begin{spacing}{0.85}
				\printbibliography[heading=none]
			\end{spacing}
			\vspace{-1em}
		}

		\headerbox{Development cycle}{name=development,below=morphtrans}{
			%(1) look at frequency list --> check word --> if it's missing stem, add --> (1) ; if it's bad phonology --> fix phonology --> (1)
			\begin{tikzpicture}[node distance = 2cm, auto]
				% Place nodes
				\node [block] (init) {analyse corpus};
				\node [cloud, left of=init] (addstem) {add stem};
				\node [cloud, right of=init] (fixphon) {fix phonology};
				\node [block, below of=init] (freq) {examine frequency list};
				%\node [block, below of=identify] (evaluate) {evaluate candidate models};
				%\node [block, left of=evaluate, node distance=3cm] (update) {update model};
				\node [decision, below of=freq] (decide) {cause for unanalysed forms?};
				%\node [block, below of=decide, node distance=3cm] (stop) {stop};
				% Draw edges
				\path [line] (init) -- (freq);
				\path [line] (freq) -- (decide);
				\path [line] (decide) -| node [near start] {missing stem} (addstem);
				\path [line] (decide.east) -| node [near start] {bad phonology} (fixphon);
				\path [line,dashed] (addstem) -- (init);
				\path [line,dashed] (fixphon) -- (init);
			\end{tikzpicture}
		}

>>>>

\usepackage{tikz}
\usetikzlibrary{shapes,arrows} %for flowchart
% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=iumint, 
    text width=5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=iulimestone, 
    text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=iumidnight, text=grey, node distance=3cm,
    minimum height=2em]
%\usepackage{pgfbaselayers}
%\pgfdeclarelayer{background}
%\pgfdeclarelayer{foreground}
%\pgfsetlayers{background,main,foreground}

@@

\definecolor{bordercol}{RGB}{0,0,0}
%\definecolor{headercolone}{RGB}{6,130,22}
\definecolor{headercol}{cmyk}{1,0.64,0,0.6}
%\definecolor{headercolone}{cmyk}{1,0.64,0,0.6}
%\definecolor{headercoltwo}{cmyk}{0.44,0,0.15,0.17}
%\definecolor{headercolone}{cmyk}{0.3,0,0.15,0.17}
%\definecolor{headercoltwo}{cmyk}{0.3,0,0.15,0.17}
\definecolor{iumint}{cmyk}{0.40,0,0.23,0}
\definecolor{iumidnight}{cmyk}{0.71,0.30,0.13,0.41}
\definecolor{iulimestone}{cmyk}{0.11,0.13,0.14,0.26}
%\definecolor{boxcolor}{RGB}{176,208,223}
%\definecolor{boxcolor}{cmyk}{0.3,0.08,0.08,0.1}
\definecolor{boxcolor}{cmyk}{0.2,0.03,0.03,0.1}
\definecolor{headerfontcol}{RGB}{255,255,255}
\newcommand{\hilitetwo}[1]{{\addfontfeature{Color=99333399}#1}}
\newcommand{\hiliteone}[1]{{\addfontfeature{Color=06821699}#1}}
\newcommand{\hilitegrey}[1]{{\addfontfeature{Color=77777799}#1}}
\newcommand{\hilitelightgrey}[1]{{\addfontfeature{Color=CCCCCC99}#1}}
\newcommand{\hiliteblue}[1]{{\addfontfeature{Color=44697DFF}#1}}

@@

%\usepackage{natbib}
\usepackage[backend=biber,citestyle=apa,style=authoryear,maxbibnames=99,maxcitenames=2]{biblatex}
\bibliography{poster}
\renewcommand*{\nameyeardelim}{\addcomma\space}
\renewcommand*{\bibfont}{\footnotesize}

@@

		\headerbox{References}{name=references,column=3,below=tuvanvowelharmony}{
			\begin{spacing}{0.7}
				\printbibliography[heading=none]
			\end{spacing}
			\vspace{-0.5em}
		}

		\headerbox{Development cycle}{name=development,below=morphtrans}{
			%(1) look at frequency list --> check word --> if it's missing stem, add --> (1) ; if it's bad phonology --> fix phonology --> (1)
			\scalebox{0.8}{
			\begin{tikzpicture}[node distance = 2cm, auto]
				% Place nodes
				\node [block] (init) at (1,3) {analyse corpus} ;
				\node [cloud, left of=init] (addstem) at (0,3) {add stem};
				\node [cloud, right of=init] (fixphon) at (2,3) {fix phonology};
				\node [block, below of=init] (freq) at (1,2) {examine frequency list};
				\node [decision, right of=freq] (break) at (1.5,0) {did something break?};
				%\node [block, below of=identify] (evaluate) {evaluate candidate models};
				%\node [block, left of=evaluate, node distance=3cm] (update) {update model};
				\node [decision, below right of=freq] (decide) at (0,-1) {cause for unanalysed forms?};
				%\node [block, below of=decide, node distance=3cm] (stop) {stop};
				% Draw edges
				\path [line] (init) -- (freq);
				\path [line] (freq) -- (break);
				\path [line] (break.south) -| node [near start] {no} (decide.north) ;
				\path [line] (break.north) -| node [near start] {yes}(fixphon.south) ;
				\path [line] (decide) -| node [near start] {missing stem} (addstem);
				\path [line] (decide.east) --(decide-|fixphon.east) node [below, midway] {bad phonology} |-(break.north-|fixphon.south) -- (fixphon.south);
				\path [line,dashed] (addstem) -- (init);
				\path [line,dashed] (fixphon) -- (init);
			\end{tikzpicture}}
		}
